Replication on multicore considering hierarchy and characteristics of the network

### 2013-04-10 paper.tex
Added algorithm2e LaTeX module

\begin{algorithm}[H]
  %
  \SetKwInOut{Assumptions}{assumptions}
  \Assumptions{Processes have unique contiguous
    identifiers starting at 0}
  \BlankLine
  %
  \SetKwArray{c}{channels}
  \SetKwFunction{connectNode}{connectNode}
  \SetKwFunction{listen}{listen}
  % 
  \KwData{process id $p$, round $r$, %
    each process an array of channels \c}
  \KwResult{Fully-meshed network of processes}
  % 
  \BlankLine
  %
  $r \leftarrow 0$\;
  \For{$i \leftarrow 0$ \KwTo $num(p)$}{
    \eIf{$p=i$}{
      \For{$o \leftarrow i+1$ \KwTo $num(p)$}{
        \c{$o$} $\leftarrow$ \connectNode{$o$}\;
      }
    }{
        \c{$i$} $\leftarrow$ \listen{}\;
    }
  }
  \caption{Atomic broadcast on reliable communication channels}
  \label{algo:ab}
\end{algorithm}

@@

\begin{algorithm}[H]
  \SetAlgoLined
  %
  \KwData{List of processes $p$, broadcast tree as graph $(V, E)$}
  \KwResult{Tree based atomic broadcast using a sequentializer}
  % 
  $(V, E)$ = build\_graph\;
  \While{not at end of this document}{
    read current\;
    \eIf{understand}{
      go to next section\;
      current section becomes this one\;
    }{
      go back to the beginning of current section\;
    }
  }
  \caption{Atomic broadcast on reliable communication channels}
  \label{algo:ab}
\end{algorithm}

>>>>

This is required for Barrelfish UMP communication channels since on
bind, no source identifier is send along\footnote{Check if this is
  actually true, and even if it is true, if is a Barrelfish problem,
  and not a general one}.

\begin{algorithm}[H]
  %
  \SetKwInOut{Assumptions}{assumptions}
  \Assumptions{Processes have unique contiguous
    identifiers starting at 0}
  \BlankLine
  %
  \SetKwArray{c}{channels}
  \SetKwFunction{connectNode}{connectNode}
  \SetKwFunction{listen}{listen}
  \SetKwFunction{barrier}{barrier}
  % 
  \KwData{process id $p$, round $r$, %
    each process an array of channels \c}
  \KwResult{Fully-meshed network of processes}
  % 
  \BlankLine
  %
  $r \leftarrow 0$\;
  \For{$i \leftarrow 0$ \KwTo $num(p)$}{
    \eIf{$p=i$}{
      \For{$o \leftarrow i+1$ \KwTo $num(p)$}{
        \c{$o$} $\leftarrow$ \connectNode{$o$}\;
      }
    }{
        \c{$i$} $\leftarrow$ \listen{}\;
    }
    \barrier{} \tcp*{Otherwise, reordering possible}
  }
  \caption{Establish fully-meshed network of channels}
  \label{algo:ab_bindOB}
\end{algorithm}

@@

\begin{algorithm}[H]
\SetKwProg{Fn}{Function}{}{end}%
\SetKwFunction{receive}{receive}%
\SetKwFunction{send}{send}%
  %
  \KwData{List of processes $p$, broadcast tree as graph $(V, E)$}
  \KwResult{Tree based atomic broadcast using a sequentializer}
  % 
  \BlankLine
  \Fn(\tcp*{Receive a message}){\receive{$m$}}{
    $i \leftarrow 5$
    \tcp{Receive a message}
  }
  % 
  \BlankLine
  \Fn(\tcp*{Send a message}){\send{void}}{
    $i \leftarrow 5$
  }
  \caption{Atomic broadcast on reliable communication channels}
  \label{algo:ab}
\end{algorithm}
